Joint Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2024-02-21 src/tex/ms.tex
[showyourwork] overleaf sync

    \begin{figure}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/gmm-eigen-images.pdf}
            \caption{
                Sum of Eigenimages weighted by their corresponding Eigenvalue of the covariance matrices of the first $32$ components of the GMM learned from the JWST Cas A image. The color scale varies between the images, so their contrast is different. 
            }
            \label{fig:gmm-eigen-images}
            \script{gmm-eigen-images.py}
        \end{centering}
    \end{figure}

>>>>

    \begin{figure}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/gmm-eigen-images.pdf}
            \caption{
                Example Eigenimages of the covariance matrices of the GMM learned from the JWST Cas A image. The figure shows the first six Eigenvectors, reshaped as images, of the GMM components $\{105, 77, 17\}$ (same as Figure~\ref{fig:patches}), in descending order of the value of their corresponding Eigenvalue. The color scale varies between the images, so their contrast is different. 
            }
            \label{fig:gmm-eigen-images}
            \script{gmm-eigen-images.py}
        \end{centering}
    \end{figure}
